---
title: "Norming_analysis"
author: "Will Clapp"
date: "6/23/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(psych)
```




```{r}
df.cat_people <- read.csv("/Users/willclapp/Desktop/QP1/QP1norming/cat_norming/mturk/experiment-subject_information.csv")

df.exposure_people <- read.csv("/Users/willclapp/Desktop/QP1/QP1norming/exposure_norming/mturk/experiment-subject_information.csv")

df.mp_people <- read.csv("/Users/willclapp/Desktop/QP1/QP1norming/mp_norming/mturk/experiment-subject_information.csv")

df.cat <- read.csv("/Users/willclapp/Desktop/QP1/QP1norming/cat_norming/mturk/experiment-trials.csv")

df.exposure <- read.csv("/Users/willclapp/Desktop/QP1/QP1norming/exposure_norming/mturk/experiment-trials.csv")

df.mp <- read.csv("/Users/willclapp/Desktop/QP1/QP1norming/mp_norming/mturk/experiment-trials.csv")
```



```{r}
df.subjects <- rbind(df.cat_people, df.exposure_people, df.mp_people)

summary(df.subjects)

```

Recode so that 0 = voiceless and 1 = voiced
```{r}
df.cat <- df.cat %>% 
  mutate("response_01" = ifelse(response == "voiced", 1, 0))

df.exposure <- df.exposure %>% 
  mutate("response_01" = ifelse(response == "voiced", 1, 0))

df.mp <- df.mp %>% 
  mutate("response_01" = ifelse(response == "voiced", 1, 0))
```



Filter out bad participants from categorization. Cut off time 6 minutes. One participant gone.


```{r}
summary(df.cat)

df.cat_bad <- df.cat %>% 
  filter(Answer.time_in_minutes < 6)

df.cat_good <- df.cat %>% 
  filter(Answer.time_in_minutes > 6)
```

Separate into coda and onset where onset is slide_order < 84

```{r}
df.cat_onset <- df.cat_good %>% 
  filter(slide_order < 84)

df.cat_coda <- df.cat_good %>% 
  filter(slide_order > 84)

```



Visualize all for categorization
```{r}
df.mean_cat_onset <- df.cat_onset %>% 
  group_by(set, step) %>% 
  summarise(response = mean(response_01))

df.mean_cat_coda <- df.cat_coda %>% 
  group_by(set, step) %>% 
  summarise(response = mean(response_01))

ggplot(data = df.mean_cat_onset,
       mapping = aes(x = step,
                     y = response)) +
  geom_point() +
  geom_hline(yintercept=0.5) +
  geom_smooth(method = "lm") +
  facet_wrap(~set) +
  ylim(0,1) +
  scale_x_continuous(breaks = seq(0,30,1))

ggplot(data = df.mean_cat_coda,
       mapping = aes(x = step,
                     y = response)) +
  geom_point() +
  geom_hline(yintercept=0.5) +
  geom_smooth(method = "lm") +
  facet_wrap(~set) +
  ylim(0,1) +
  scale_x_continuous(breaks = seq(0,30,1))



```


Filter out bad participants from exposure. Cut off time 10 minutes. Two participants gone.


```{r}
summary(df.exposure)

ggplot(data = df.exposure,
       mapping = aes(x = workerid,
                     y = Answer.time_in_minutes)) + 
  geom_point()

df.exp_bad <- df.exposure %>% 
  filter(Answer.time_in_minutes < 10)

df.exp_good <- df.exposure %>% 
  filter(Answer.time_in_minutes > 10)
```

slideorder less than 200

```{r}
df.exp_word <- df.exp_good %>% 
  filter(slide_order < 200)

df.exp_nonword <- df.exp_good %>% 
  filter(slide_order > 200)

```

Visualize all for exposure
```{r}
df.mean_exp_word <- df.exp_word %>% 
  group_by(set, step) %>% 
  summarise(response = mean(response_01))

df.mean_exp_nonword <- df.exp_nonword %>% 
  group_by(set, step) %>% 
  summarise(response = mean(response_01))


ggplot(data = df.mean_exp_word,
       mapping = aes(x = step,
                     y = response)) +
  geom_point() +
  geom_hline(yintercept=0.5) +
  geom_smooth(method = "lm") +
  facet_grid(~set) +
  ylim(0,1) +
  scale_x_continuous(breaks = seq(0,30,1))

ggplot(data = df.mean_exp_nonword,
       mapping = aes(x = step,
                     y = response)) +
  geom_point() +
  geom_hline(yintercept=0.5) +
  geom_smooth(method = "lm") +
  facet_wrap(~set) +
  ylim(0,1) +
  scale_x_continuous(breaks = seq(0,30,1))



```





STart for minimal pairs

Filter out bad participants. Cut off time 16 minutes. No participants gone


```{r}
summary(df.mp)

ggplot(data = df.mp,
       mapping = aes(x = workerid,
                     y = Answer.time_in_minutes)) + 
  geom_point()

```

<!-- path first  -->

<!-- ```{r} -->
<!-- df.mp_onset <- df.mp %>%  -->
<!--   filter(path[1] == 'b') -->

<!-- df.exp_nonword <- df.exp_good %>%  -->
<!--   filter(slide_order > 200) -->

<!-- ``` -->

Visualize all for mp
```{r}
df.mean_mp <- df.mp %>% 
  group_by(set, step) %>% 
  summarise(response = mean(response_01))



ggplot(data = df.mean_mp,
       mapping = aes(x = step,
                     y = response)) +
  geom_point() +
  geom_hline(yintercept=0.5) +
  geom_smooth(method = "lm") +
  facet_wrap(~set) +
  ylim(0,1) +
  scale_x_continuous(breaks = seq(0,30,1))





```
